Quantile Forecast Matching with a Bayesian Quantile Gaussian Process Model

### 2025-08-21 response.tex

\documentclass{article}

\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{amsmath}
% \usepackage{amsfonts}

\usepackage{xcolor}
\newcommand{\jarad}[1]{{\color{red} Jarad: #1}}
\newcommand{\spencer}[1]{{\color{blue} Spencer: #1}}

\begin{document}

\section*{Reviewer 1}

The paper presents a Gaussian process model for quantiles, called quantile GP, which is based on
quantile functions and sample quantiles. The QGP is estimated from a Bayesian perspective in
both simulation studies and a real data application. In particular, the authors employ the QGP to
approximate the distributions of quantile forecasts from the 2023-24 US Centers for Disease Control
collaborative flu forecasting initiative.

Below, you find my detailed comments.

\subsection*{Major Comments}

\begin{itemize}
  \item The introduction is weak and does not clearly communicate the contribution of the paper relative
  to the existing literature. It is difficult to understand the motivation for using a Quantile Gaussian
  process (QGP) over other methods such as an order statistics based model. I strongly recommend
  to completely rewrite the introduction to clearly explain the novelty of the paper and the key
  results.

  \item On page 10, when defining $\psi_{i,j}$ , should the subscript i and j enter in the right-hand side of the
  formula, particularly in $p$ and $p'$?

  \spencer{Fixed}

  \item In both the inferential and empirical parts, the authors refer to an unknown n. In what context
  is the sample size considered unknown?

  \item In Equation 16, what does $L$ represent? Moreover, what should $UWD1$ tells to the reader in
  comparison to $W_D$ or $p -W_D$?

  \spencer{Fixed}

  \item Regarding the different distance measures used, there seems to be redundancy. It may be better to
  avoid including all of them and instead consider incorporating other relevant metrics for evaluating
  quantiles and densities, such as the quantile CRPS (qCRPS, Gneiting, T., and Ranjan, R. (2011,
  JBES)) or the ACPS (Iacopini et al, (2023, JBES)).

  \spencer{Ignore}

  \item In Section 4.1.1, the choice of a truncated normal prior for $\sigma$ is unclear. Why did the authors not
  consider an Inverse Gamma or a Gamma prior? Moreover, how do the authors justify the choice
  of a prior center near the real data ($\mu = 4$ and prior $\mu \sim N(5, 7^2)$? For the prior on $n$, which
  appears to represent the sample size (assumed to be an integer), why is a Normal distribution
  used instead of a Uniform or Categorical distribution?

  \spencer{Responded}

  \item Although, the authors state that Bayesian inference is employed, it is unclear how $n$ estimated
  within the QGP framework. It would also be interested to present trace plots for the parameters
  and provide some convergence diagnostics.

  \spencer{Ignore}

  \item On page 17, what is $\theta^*_m$?

  \spencer{Clarified}

  \item When defining $\widehat{KLD}$, what does S denote?

  \spencer{Clarified}

  \item What is the main takeaway from Section 4.1.1? It appears that a simpler model (ORD) yields
  better results that the proposed QGP across different sample size and parameters estimators.

  \spencer{Responded}

  \item In Section 4.2, did the authors run some robustness check for different choices of C? Similarly to
  my previous point, why were the prior distribution not chosen as an inverse Gamma and centered
  differently? I assume that $\alpha$ = ($\alpha_1, . . . , \alpha_C$), is this correct? Furthermore, why are the results not
  compared with the best performing model from Section 4.1.1. i.e. the ORD model?

  \item In the real data application, what is the value of $n$? Figure 5 and 6 are quite difficult to interpret.
  I was expecting a comparison with other methods, as done in the simulation study, potentially
  using metrics such as the qCRPS. Instead, only two metrics are compared, without explaining
  well what is happening to the dots and what are they referring to.
  \end{itemize}

\subsection*{Minor Comments}

  \begin{itemize}
  \item The writing is still conversational and the English is really poor and full of mistakes. For example,
  the authors use intensively the word “this” along the paper. Moreover, page 5 “the CDF and
  PDF are more used often for modeling and inference”; end of page 9, what does the sentence
  “But when these functions belong...” mean? Page 13, “to assess the how well...”; or “the the
  CDF ...”. On page 16 ,“decrase”

  \item Please include the formula along the text and not between dots. F.e. “the p-WD in terms of the
  corresponding QFs is defined in (15)”. should become “ the $p-WD$ in terms of the corresponding
  QFs is defined as...”. It is an example, but mainly all the equation needs to follow a similar
  specification.

  \end{itemize}

\end{document}

### 2025-09-26 manuscript.tex
springer journal format added

%% 
%% Copyright 2007-2024 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.3 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

\documentclass[preprint,12pt,authoryear]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times,authoryear]{elsarticle}
%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,3p,times,authoryear]{elsarticle}
%% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,5p,times,authoryear]{elsarticle}
%% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
% \usepackage{amssymb}
%% The amsmath package provides various useful equation environments.
% \usepackage{amsmath}
\usepackage{amsmath,amsthm,amssymb,scrextend,mathtools}
% \usepackage{hyperref}
% \usepackage{newtxmath} %for making indicator function
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\usepackage{natbib}
\usepackage{lmodern} %%helps deal with font size problems
\usepackage{dsfont}
\newcommand{\1}[1]{\mathds{1}\left[#1\right]}

\newcommand{\jarad}[1]{{\color{red} ?? Jarad: #1}}

\journal{Computational Statistics and Data Analysis}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}

\title{Quantile Forecast Matching with a Bayesian Quantile Gaussian Process Model} %% Article title

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

\author[label1]{Spencer Wadsworth} %% Author name
\author[label1]{Jarad Niemi}

%% Author affiliation
\affiliation[label1]{organization={Iowa State Univerity, Department of Statistics},%Department and Organization
            addressline={2438 Osborn Dr}, 
            city={Ames},
            postcode={50011}, 
            state={Iowa},
            country={USA}}

%% Abstract
\begin{abstract}
A set of probabilities along with corresponding quantiles are often used to 
define predictive distributions or probabilistic forecasts. These quantile 
predictions offer easily interpreted uncertainty of an event, 
and quantiles are generally straightforward to estimate using standard 
statistical and machine learning methods. However, compared to a distribution 
defined by a probability density or cumulative distribution function, a set of 
quantiles has less distributional information. When given estimated 
quantiles, it may be desirable to estimate a fully defined continuous 
distribution function. Many researchers do so to make evaluation or 
ensemble modeling simpler. Most existing methods for fitting a distribution to 
quantiles lack accurate representation of the inherent uncertainty from 
quantile estimation or are limited in their applications. In this manuscript, we 
present a Gaussian process model, the quantile Gaussian process, which is based 
on established theory of quantile functions and sample quantiles, to construct 
a probability distribution given estimated quantiles. A Bayesian application of 
the quantile Gaussian process is evaluated for parameter inference and 
distribution approximation in simulation studies. The quantile Gaussian 
process is used to approximate the distributions of quantile forecasts from the 
2023-24 US Centers for Disease Control collaborative flu forecasting 
initiative. The simulation studies and data analysis show that the quantile 
Gaussian process leads to accurate inference on model parameters, estimation of 
a continuous distribution, and uncertainty quantification of sample quantiles.
\end{abstract}

%%Graphical abstract
% \begin{graphicalabstract}
%\includegraphics{grabs}
% \end{graphicalabstract}

%%Research highlights
% \begin{highlights}
% \item Research highlight 1
% \item Research highlight 2
% \end{highlights}
% 
%% Keywords
\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
% 
% %% PACS codes here, in the form: \PACS code \sep code
% 
% %% MSC codes here, in the form: \MSC code \sep code
% %% or \MSC[2008] code \sep code (2000 is the default)
Sample quantiles \sep Quantile regression \sep Probabilistic forecasting \sep 
Disease outbreaks
\end{keyword}
% 
\end{frontmatter}

%% Add \usepackage{lineno} before \begin{document} and uncomment 
%% following line to enable line numbers
%% \linenumbers

%% main text
%%

@@

The asymptotic distribution of a set of sample quantiles is given in 
(\ref{eq:qclt}), and it is the basis for the QGP model for QM in section 
\ref{sec:qgp_model}. For independent draws $Y_1, ..., Y_n$ from a continuous 
random variable with CDF $F$, PDF $f$, and QF $Q$, and with a set of sample 
quantiles calculated by (\ref{eq:quant_df}), theorem \ref{thm:qclt} holds. 
Note that in (\ref{eq:qclt}), $N_K(\cdot, \cdot)$ refers to a multivariate 
normal distribution with $K$ dimensions, 
\jarad{Include the mean and covariance matrix in this definition? I think we should.}
and in (\ref{eq:qclt_covariance}) the 
operator $a \wedge b$ is the minimum of the values $a$ and $b$.
\jarad{Do we need to be concerned about the order of operations when using $\wedge$? I believe $p_i \wedge p_j - p_i p_j = (p_i \wedge p_j) - p_i p_j$, but it could be $p_i \wedge p_j - p_i p_j = p_i \wedge (p_j - p_i p_j)$.
Using the $()$ would make it clear without having to define the order of operations.}

@@

\[
    \Psi_{ij} = \frac{2 \pi (p\wedge p' - p p')}{\text{exp}\{-\frac{1}{2}[\Phi^{-1}(p)^2 + \Phi^{-1}(p')^2]\}}.
\]
Model (\ref{eq:norm_qgp}) can then be viewed as an atypical normal linear 
regression model. Two aspects that make this model atypical relative to the 
standard linear regression model are that the slope parameter $\sigma$ must be 
greater than 0 and that $\sigma$ is both a regression coefficient and part of 
the variance.
% making $\sigma$ unidentifiable.
Note also that the sample size $n$ is included as part of the variance. If $n$ 
is known, then it may be multiplied through $\Psi$ and forgotten. If unknown, 
it can then be accounted for as an unknown part of the variance.

@@

\begin{equation}
    \label{eq:wass_dist_quant}
    WD_p (F, G) = \left( \int_0^1 |F^{-1}_X(t) - G^{-1}_Y(t)|^p dt \right)^{1/p}
\end{equation}

We define a modified version of the WD, the uniform 1-WD (UWD1) in 
(\ref{eq:pit_wass_dist}). Here we take $F_X$ to be the CDF of a continuous 
random variable $X$. For a different continuous random variable $\xi$ with CDF 
$F_{\xi}$, $F_X(\xi)$ is a random variable with support on $[0,1]$. We let 
$F_{X,\xi}$ be the CDF of the random variable $F_X(\xi)$. Then the measure in 
(\ref{eq:pit_wass_dist}) is a measure of how close $F_X(\xi)$ is the the CDF of 
a standard uniform distribution, noting that by the PIT, if 
$\xi \overset{D}{=} X$, $F_X(\xi)$ is the random variable of a standard uniform 
distribution. Multiplying the integral in (\ref{eq:pit_wass_dist}) by two 
ensures the measure takes values between 0 and 1 
\cite[]{645854} \jarad{I think the URL should be in the citation not here. Also, is this mentioned anywhere else so that we don't have to cite stackexchange?}
where a value near 0 means $\xi$ and $X$ are ``near'' each other.

\begin{equation}
    \label{eq:pit_wass_dist}
    UWD_1(F, \mathcal{L}) = 2\int_0^1 |F_{X,\xi} (x) - x|dx
\end{equation}

@@

\subsubsection{Normal parameter estimation}
In this simulation study, we fit the ORD and IND models to quantiles estimated 
from independent samples from a normal distribution and compare parameter 
estimation with fits from the QGP model. Quantiles were simulated by first 
drawing a sample of size $n$ from a known distribution then estimating $K$ 
quantiles given probabilities $\{p_1, ..., p_K\}$. The ORD, IND, and QGP models 
were then fit to the quantiles where $F$ was set to be the CDF of a normal 
distribution. For each of 
$n \in \{50; 150; 500; 1{,}000; 5{,}000\}$ and 
% $K \in \{3,7,15,50\}$
$K = 23$, there 
were 500 simulation replicates. The data were simulated from a normal 
distribution with mean $\mu = 4$ and standard deviation $\sigma = 3.5$.
For each of QGP, ORD, and IND models, we assigned the same prior distributions 
to $\mu$ and $\sigma$. When $n$ is unknown, we also assigned it a prior 
distribution. The prior distributions were $\mu \sim N(5,7^2)$, 
$\sigma \sim N(0, 6^2) \mathds{1} \{\sigma > 0\}$, and
$n \sim N(0,3000^2)\mathds{1}\{n > 0\}$.
% \begin{align*}
%     \mu &\sim N(5,7^2) \\
%     \sigma &\sim N(0, 6^2) \mathds{1}\{\sigma > 0\}\\
%     n &\sim N(0,3000^2)\mathds{1}\{n > 0\}.
% \end{align*}
For the IND model the prior on the independent parameter 
$\sigma_{\rho}\mathds{1}\{n > 0\}$ from model (\ref{eq:ind_quantile}) is 
$1/\sigma_{\rho} \sim N(0, 3000^2)$, 
\jarad{Shouldn't this prior be strictly positive?}
which is similar to the prior on $n$ for 
the QGP and ORD models. For each fit, the HMC chain was run for 60,000 draws 
with the first 10,000 discarded as a burn-in.

@@

To analyze how well QM methods produced predictive distributions which 
approximate the true distribution $N(4, 3.5^2)$, we measured the distance 
between the estimated predictive distributions of QGP, ORD, and IND fits to 
the true distribution. 
We also measured the distances of the SPL and KDE QM fits to the true 
distribution. The distances were measured via the UWD1, TV, and KLD metrics. 
The UWD1 for each of QGP, ORD, QGP-n, ORD-n, and IND were calculated as 
follows. For $\{\theta_m\}^M$ being $M$ draws from the posterior distribution
of $\theta$ where $\theta_m = (\mu_m, \sigma_m)$, the QM posterior predictive 
distribution was simulated by repeatedly sampling a $\theta_m^*$, then sampling 
$X_m$ from a distribution with CDF $F_{\theta_m^*}$. Repeating this for 
$M = 50,000$ times gives a QM posterior predictive sample. For the CDF 
$F_{\theta}$ where $\theta$ is the true parameter, $\xi_m = F_{\theta}(X_m)$ 
was calculated and the empirical CDF $\hat{F}_{\xi}$ was calculated from the 
sample $\{\xi_m\}^M$. $F_{\xi}$ in (\ref{eq:pit_wass_dist}) was then replaced 
by $\hat{F}_{\xi}$ to calculate UWD1. For SPL and KDE $F_{\xi}(x)$ was replaced 
by the respective estimated CDFs. The \texttt{integrate} function in \texttt{R} 
was used for calculating the UWD1 in (\ref{eq:pit_wass_dist}).

@@

\[
    \widehat{KLD}(f_{\theta} || f_{\Bar{\theta}_M}) = 
    \frac{1}{S}\sum_{s = 1}^S \text{log} 
    \left(\frac{f_{\theta}(Y_s)}{f_{\Bar{\theta}_M}(Y_s)}\right)
\]
where $Y_s \overset{iid}{\sim} F_{\theta}$. For both SPL and KDE, 
$f_{\Bar{\theta}_M}$ is the estimated PDF.

@@

This study shows the ability of the QGP QM model to estimate and perform 
inference on model parameters where the true distribution family is known. It 
also shows the QGP's ability to produce a posterior predictive distribution 
which closely matches a true distribution, according to several metrics, 
relative to other QM methods. Between parameter inference and predicting the 
true distribution, QGP is superior to all methods we compared it with except 
for the ORD model which has similar results to the QGP. 
Additional plots for this study and for a similar simulation 
study where the data was simulated from an exponential family distribution are 
in the supplementary materials.
% \ref{app:extra_sim}. 
The results of the exponential family study are similar to those of the 
normal distribution family study.

@@

The analysis above show the usefulness in using the QGP model both in parameter 
estimation and in QM when given sample quantiles. In the normal case, the QGP 
showed improved parameter inference over the IND model and allows for making 
inference on the sample size $n$. Compared to the SPL and KDE QM methods, the 
QGP fits tend to be closer in distance to the true distribution. The QGP model, 
however, performs about the same as the ORD model in terms of inference and QM. 
The section below outlines a situation where the QGP model may be a better 
option for QM than the ORD model.

@@

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
\appendix
\section{Example Appendix Section}
\label{app1}

Appendix text.

@@

% \begin{thebibliography}{00}
% 
% %% For authoryear reference style
% %% \bibitem[Author(year)]{label}
% %% Text of bibliographic item
% 
% \bibitem[Lamport(1994)]{lamport94}
%   Leslie Lamport,
%   \textit{\LaTeX: a document preparation system},
%   Addison Wesley, Massachusetts,
%   2nd edition,
%   1994.
% 
% \end{thebibliography}
\end{document}

\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

>>>>

@@

The asymptotic distribution of a set of sample quantiles is given in 
(\ref{eq:qclt}), and it is the basis for the QGP model for QM in section 
\ref{sec:qgp_model}. For independent draws $Y_1, ..., Y_n$ from a continuous 
random variable with CDF $F$, PDF $f$, and QF $Q$, and with a set of sample 
quantiles calculated by (\ref{eq:quant_df}), theorem \ref{thm:qclt} holds. 
Note that in (\ref{eq:qclt}), 
$N_K(\boldsymbol{\mu}, \boldsymbol{\Sigma})$ refers to a 
multivariate 
normal distribution with $K$ dimensions where $\boldsymbol{\mu}$ is the mean
vector and $\boldsymbol{\Sigma}$ is the covariance matrix. 
In (\ref{eq:qclt_covariance}) the 
operator $a \wedge b$ is the minimum of $a$ and $b$, with order of operations
such that $a \wedge b - ab = (a \wedge b) - ab$.

@@

\[
    \Psi_{ij} = \frac{2 \pi (p_i\wedge p_j - p_i p_j)}{\text{exp}\{-\frac{1}{2}[\Phi^{-1}(p_i)^2 + \Phi^{-1}(p_j)^2]\}}.
\]
Model (\ref{eq:norm_qgp}) can then be viewed as an atypical normal linear 
regression model. Two aspects that make this model atypical relative to the 
standard linear regression model are that the slope parameter $\sigma$ must be 
greater than 0 and that $\sigma$ is both a regression coefficient and part of 
the variance.
% making $\sigma$ unidentifiable.
Note also that the sample size $n$ is included as part of the variance. If $n$ 
is known, then it may be multiplied through $\Psi$ and forgotten. If unknown, 
it can then be accounted for as an unknown part of the variance.

@@

\begin{equation}
    \label{eq:wass_dist_quant}
    WD_p (F_X, F_Y) = \left( \int_0^1 |F^{-1}_X(t) - F^{-1}_Y(t)|^p dt \right)^{1/p}
\end{equation}

We define a modified version of the WD, the uniform 1-WD (UWD1) in 
(\ref{eq:pit_wass_dist}). Here we take $F_X$ to be the CDF of a continuous 
random variable $X$. For a different continuous random variable $\xi$ with CDF 
$F_{\xi}$, $F_X(\xi)$ is a random variable with support on $[0,1]$. We let 
$F_{X,\xi}$ be the CDF of the random variable $F_X(\xi)$. Then the measure in 
(\ref{eq:pit_wass_dist}) measures how close $F_X(\xi)$ is the the CDF of 
a standard uniform distribution with CDF $\mathcal{U}$, 
noting that by the PIT, if 
$\xi \overset{D}{=} X$, $F_X(\xi)$ is the random variable of a standard uniform 
distribution. The integral in (\ref{eq:pit_wass_dist}) takes values between
0 and 1/2 \cite[]{645854}, and multiplying by two 
ensures the measure takes values between 0 and 1. This makes the UWD1 more
interpretable than the WD
where a value near 0 suggests $\xi$ and $X$ are ``near'' each other, and a value
near 1 suggests they are far apart.

\begin{equation}
    \label{eq:pit_wass_dist}
    UWD_1(F_{X,\xi}, \mathcal{U}) = 2\int_0^1 |F_{X,\xi} (u) - x|du
\end{equation}

@@

\subsubsection{Normal parameter estimation}
In this simulation study, we fit the ORD and IND models to quantiles estimated 
from independent samples from a normal distribution and compare parameter 
estimation with fits from the QGP model. Quantiles were simulated by first 
drawing a sample of size $n$ from a known distribution then estimating $K$ 
quantiles given probabilities $\{p_1, ..., p_K\}$. The ORD, IND, and QGP models 
were then fit to the quantiles where $F$ was set to be the CDF of a normal 
distribution. For each of 
$n \in \{50; 150; 500; 1{,}000; 5{,}000\}$ and 
% $K \in \{3,7,15,50\}$
$K = 23$, there 
were 500 simulation replicates. The data were simulated from a normal 
distribution with mean $\mu = 4$ and standard deviation $\sigma = 3.5$.
For each of QGP, ORD, and IND models, we assigned the same prior distributions 
to $\mu$ and $\sigma$. When $n$ is unknown, we also assigned it a prior 
distribution. 
As one will generally have access to the quantiles being fit, 
it is reasonable that a informative prior $\mu$ centered near where the data is
centered be assigned. We took this approach herein, and for spread parameters,
we assigned normal priors truncated at 0 as recommended by
\cite{gelman2006prior}.
The prior distributions were $\mu \sim N(5,7^2)$,
$\sigma \sim N(0, 6^2) \mathds{1} \{\sigma > 0\}$, and
$n \sim N(0,3000^2)\mathds{1}\{n > 0\}$.
% \begin{align*}
%     \mu &\sim N(5,7^2) \\
%     \sigma &\sim N(0, 6^2) \mathds{1}\{\sigma > 0\}\\
%     n &\sim N(0,3000^2)\mathds{1}\{n > 0\}.
% \end{align*}
For the IND model the prior on the independent parameter 
$\sigma_{\rho}$ from model (\ref{eq:ind_quantile}) is 
$1/\sigma_{\rho} \sim N(0, 3000^2)\mathds{1}\{\sigma_{\rho} > 0\}$,
which is similar to the prior on $n$ for 
the QGP and ORD models. For each fit, the HMC chain was run for 60,000 draws 
with the first 10,000 discarded as a burn-in.

@@

To analyze how well QM methods produced predictive distributions which 
approximate the true distribution $N(4, 3.5^2)$, we measured the distance 
between the estimated predictive distributions of QGP, ORD, and IND fits to 
the true distribution. 
We also measured the distances of the SPL and KDE QM fits to the true 
distribution. The distances were measured via the UWD1, TV, and KLD metrics. 
The UWD1 for each of QGP, ORD, QGP-n, ORD-n, and IND were calculated as 
follows. For $\{\theta_m\}^M$ being $M$ draws from the posterior distribution
of $\theta$ where $\theta_m = (\mu_m, \sigma_m)$, the QM posterior predictive 
distribution was simulated by repeatedly sampling a $\theta_m^*$ from 
$\{\theta_m\}^M$, then sampling 
$X_m$ from a distribution with CDF $F_{\theta_m^*}$. Repeating this for 
$M = 50,000$ times gives a QM posterior predictive sample. For the CDF 
$F_{\theta}$ where $\theta$ is the true parameter, $\xi_m = F_{\theta}(X_m)$ 
was calculated and the empirical CDF $\hat{F}_{\xi}$ was calculated from the 
sample $\{\xi_m\}^M$. $F_{\xi}$ in (\ref{eq:pit_wass_dist}) was then replaced 
by $\hat{F}_{\xi}$ to calculate UWD1. For SPL and KDE $F_{\xi}(x)$ was replaced 
by the respective estimated CDFs. The \texttt{integrate} function in \texttt{R} 
was used for calculating the UWD1 in (\ref{eq:pit_wass_dist}).

@@

\[
    \widehat{KLD}(f_{\theta} || f_{\Bar{\theta}_M}) = 
    \frac{1}{S}\sum_{s = 1}^S \text{log} 
    \left(\frac{f_{\theta}(Y_s)}{f_{\Bar{\theta}_M}(Y_s)}\right)
\]
where $S$ is the total number of Monte Carlo samples and
$Y_s \overset{iid}{\sim} F_{\theta}$. For both SPL and KDE, 
$f_{\Bar{\theta}_M}$ is the estimated PDF.

@@

This study shows the ability of the QGP QM model to estimate and perform 
inference on model parameters where the true distribution family is known. It 
also shows the QGP's ability to produce a posterior predictive distribution 
which closely matches a true distribution, according to several metrics, 
relative to other QM methods. Between parameter inference and predicting the 
true distribution, QGP is superior to all methods we compared it with except 
for the ORD model which has similar results to --or for small sample size
slighty better than-- the QGP. However, we feel the QGP's linear model form is
easier to understand than the ORD model and thus preferable for interpretation.
Additional plots for this study and for a similar simulation 
study where the data was simulated from an exponential family distribution are 
in the supplementary materials.
% \ref{app:extra_sim}. 
The results of the exponential family study are similar to those of the 
normal distribution family study.

@@

The analysis above show the usefulness in using the QGP model both in parameter 
estimation and in QM when given sample quantiles. In the normal case, the QGP 
showed improved parameter inference over the IND model and allows for making 
inference on the sample size $n$. Compared to the SPL and KDE QM methods, the 
QGP fits tend to be closer in distance to the true distribution. The QGP model, 
however, performs about the same or for smaller $n$ slightly poorer than the
ORD model in terms of inference and QM. However, we feel the QGP is a simpler
model to
understand than the ORD and easier to interpret.
The following section outlines a situation where the QGP model may be a better 
option for QM than the ORD model.

@@

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
\appendix

@@

% \begin{thebibliography}{00}
% 
% %% For authoryear reference style
% %% \bibitem[Author(year)]{label}
% %% Text of bibliographic item
% 
% \bibitem[Lamport(1994)]{lamport94}
%   Leslie Lamport,
%   \textit{\LaTeX: a document preparation system},
%   Addison Wesley, Massachusetts,
%   2nd edition,
%   1994.
% 
% \end{thebibliography}
